Testing gene methylation enrichment analysis approaches using simulated data

### 2024-01-10 figs/GSE158422_simulate020_rslurm.Rmd
got rslurm working now

num_dm_sets=50
sims=100
groupsizes=c(3,5,8,12)
deltas=c(0.1,0.2,0.3,0.4,0.5)

#groupsizes=5
#deltas=0.4

@@

params %>% kbl(caption="Parameters to test") %>% kable_paper("hover", full_width = F)

@@

```{r,rungsa,eval=FALSE}

sopt1 <- list(time = '1:00:00', mem="10G")

sjob <- slurm_apply(simgsa, params, jobname = 'gsa',
  nodes = 50, cpus_per_node = 2, submit = TRUE, slurm_options = sopt1,
  genesetdatabase=gsets, myann=myann, mval=normal_mval, frac_genes=0.5,
  frac_probes=0.5, num_dm_sets=num_dm_sets,
  pkgs = rev(.packages()),
  global_objects = c("randomGeneSets", "runlimma","incorp_dm", "F1", "gsets") )

@@

```{r,runlat,eval=FALSE}

sopt1 <- list(time = '1:00:00', mem="16G")

@@

```{r,runltt,eval=TRUE}

sopt1 <- list(time = '1:00:00', mem="16G")

@@

```{r,runlaw,eval=TRUE}

sopt1 <- list(time = '1:00:00', mem="16G")

@@

```{r,runlam,eval=TRUE}

sopt1 <- list(time = '1:00:00', mem="16G")

@@

```{r,runlrm,eval=TRUE}

sopt1 <- list(time = '1:00:00', mem="16G")

@@

```{r,runalt,eval=TRUE}

sopt1 <- list(time = '1:00:00', mem="16G")

@@

```{r,runalw,eval=TRUE}

sopt1 <- list(time = '1:00:00', mem="16G")

@@

```{r,runalm,eval=TRUE}

sopt1 <- list(time = '1:00:00', mem="16G")

>>>>

num_dm_sets=50
sims=100
groupsizes=c(3,5,8,12)
deltas=c(0.1,0.2,0.3,0.4,0.5)
#groupsizes=12
#deltas=0.5

@@

str(params)

params <- params[order(params$groupsize),]

@@

```{r,rungsa}

sopt1 <- list(time = '6:00:00', mem="16G")

sjob <- slurm_apply(simgsa, params, jobname = 'gsa',
  nodes = 50, cpus_per_node = 1, submit = TRUE, slurm_options = sopt1,
  genesetdatabase=gsets, myann=myann, mval=normal_mval, frac_genes=0.5,
  frac_probes=0.5, num_dm_sets=num_dm_sets,
  pkgs = rev(.packages()),
  global_objects = c("randomGeneSets", "runlimma","incorp_dm", "F1", "gsets") )

@@

```{r,runlat}

sopt1 <- list(time = '6:00:00', mem="32G")

@@

```{r,runltt}

sopt1 <- list(time = '6:00:00', mem="32G")

@@

```{r,runlaw}

sopt1 <- list(time = '6:00:00', mem="32G")

@@

```{r,runlam}

sopt1 <- list(time = '6:00:00', mem="32G")

@@

```{r,runlrm}

sopt1 <- list(time = '6:00:00', mem="32G")

@@

```{r,runalt}

sopt1 <- list(time = '6:00:00', mem="32G")

@@

```{r,runalw}

sopt1 <- list(time = '6:00:00', mem="32G")

@@

```{r,runalm}

sopt1 <- list(time = '6:00:00', mem="32G")
